\documentclass{article}
\usepackage{graphicx}

\title{CS3338 Final Project}
\author{Bread Piece}
\date{December 2025}

\begin{document}


\begin{titlepage}
    \centering

    \vspace*{2in}

    {\LARGE \textbf{Snapshot Objectives}}\\[1.5in]
    \begin{center}
        \begin{tabular}{cccc}
            
Eddie Echegoyen & Leo Banuelos & Jeffrey Li & Kent Stark \\
        \end{tabular}
    \end{center}

    \vspace{1.2in}

    {\large April 2025}

\end{titlepage}



\section*{Snapshot Objectives}

\subsection*{Start Objective}

The starting objective of the Drone Flight Path Simulator (DFPS) project is to 
establish the foundational simulation environment and core interface needed for 
mission planners to visualize and evaluate SUAS flight paths. This initial snapshot 
focuses on implementing the essential system components required for basic mission 
planning and path visualization. This includes the following key components:

\begin{itemize}
    \item Developing an intuitive 3D visualization interface for displaying drone flight paths over terrain.
    \item Implementing basic environmental and sensor detection models for audio and visual signature estimation.
    \item Creating the ability for users to draw, upload, and modify flight paths within the interface.
    \item Establishing the software architecture for plug-in extensibility to support future mission variables and data sources.
\end{itemize}

\subsection*{1st Checkpoint Objective}

The primary objective for Snapshot 2 is to incorporate core functional features 
that allow DFPS to generate measurable mission-effectiveness outputs. This includes 
integrating environmental factors, calculating detection likelihoods, and providing 
mission success feedback based on user-defined flight paths.

\subsection*{2nd Checkpoint Objective}

The primary objective for Snapshot 3 is to expand DFPS capabilities by implementing 
user-driven customization options, including advanced mission parameters, editable 
flight-path waypoints, and enhanced sensor modeling. This checkpoint also includes 
support for saving and loading flight plans for repeated use.

\subsection*{Due Date Checkpoint}

The final objective of the concluding snapshot is to refine DFPS for improved 
usability, performance, and operational stability. This includes correcting software 
errors, optimizing visual clarity for field use, and improving interface readability 
under various lighting conditions. Minor enhancements will also be implemented to 
support smoother mission-planning workflows and prepare the system for demonstration 
and evaluation.

\end{document}
