\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\setstretch{1.15}

\title{Design Specifications\\[0.5em]
SUAS Flight Path Visualization}
\author{
  Leo Banuelos \and
  Eddie Echegoyen \and
  Jeffrey Li \and
  Kent Stark
}

\begin{document}
\maketitle

\section{Overview}

This document is a simple design spec for the SUAS Flight Path Visualization
project. It lists the main pages, parts, tools, and the basic stuff that would
go into a Docker container to run the project.

\section{Pages / Screens}

\subsection*{1. Landing / Login Page}
\begin{itemize}
  \item Simple welcome text.
  \item Username / password fields (or placeholder for login).
  \item Button to enter the main app.
\end{itemize}

\subsection*{2. Mission Dashboard}
\begin{itemize}
  \item List of saved missions (name, date).
  \item Button to create a new mission.
  \item Button to open or delete a mission.
\end{itemize}

\subsection*{3. Map / 3D View Page}
\begin{itemize}
  \item 2D map view with terrain.
  \item 3D view toggle for terrain visualization.
  \item Tools to add, move, and delete waypoints.
  \item Display of current path (lines between waypoints).
\end{itemize}

\subsection*{4. Mission Info Panel}
\begin{itemize}
  \item Name and short description of the mission.
  \item Total distance and simple time estimate.
  \item Selected drone type.
  \item Simple risk indicator (for example: low / medium / high).
\end{itemize}

\subsection*{5. Settings / About}
\begin{itemize}
  \item Basic app information.
  \item Links to Jira board and GitHub repo.
\end{itemize}

\section{Main Parts of the System}

\subsection*{Frontend}
\begin{itemize}
  \item Single-page web app.
  \item Handles all user interaction.
  \item Renders the map and 3D view.
\end{itemize}

\subsection*{Backend}
\begin{itemize}
  \item Simple web API (HTTP + JSON).
  \item Endpoints to save and load missions.
  \item Stores and returns mission data.
\end{itemize}

\subsection*{Data Storage}
\begin{itemize}
  \item Missions with ID, name, description, date.
  \item List of waypoints (latitude, longitude, altitude).
  \item Optional table / collection for drone presets.
\end{itemize}

\section{Tools, Packages, and Libraries}

\subsection*{Frontend Libraries}
\begin{itemize}
  \item React (for UI).
  \item Mapbox GL JS (map view).
  \item three.js (3D visualization).
  \item Turf.js (simple geometry / distance helpers).
\end{itemize}

\subsection*{Backend / General}
\begin{itemize}
  \item Node.js
  \item npm (package manager)
  \item Express (basic web server / API)
\end{itemize}

\subsection*{Development Tools}
\begin{itemize}
  \item Git and GitHub for version control.
  \item Jira for task tracking.
\end{itemize}

\section{Docker Container Contents}

If we put this project in a Docker container, it would roughly need:

\begin{itemize}
  \item Base image: \texttt{node:lts} (Node.js + npm).
  \item System packages required by map / 3D libraries (as needed).
  \item Project source code (frontend and backend).
  \item \texttt{package.json} with all npm dependencies.
  \item Build step for frontend (for example: \texttt{npm run build}).
  \item Command to start the backend server (for example: \texttt{npm start}).
\end{itemize}

This list is enough for a basic setup. Extra tools or services can be added
later if needed.

\end{document}
